### 2016-12-22 Writing/draft.tex
Updated rate parameter in methods

For each character, both models (HKY-binary or M$k$) where chosen randomly and ran with an overall evolutionary rate drawn from a gamma distribution ($\beta$ = $100$ and $\alpha$ = $3$).
This low evolutionary rate values allowed to reduce the number of homoplasic character changes and thus reinforce the phylogenetic information in the matrices.
We resimulated every invariant characters to obtain a matrix with no invariant characters.
To ensure the that our simulation where reflecting the same parameters as real data, we only selected matrices with Consistency Indices superior to $0.26$ \citep{OReilly20160081}.

>>>>

For each character, both models (HKY-binary or M$k$) where chosen randomly and ran with an overall evolutionary rate drawn from a gamma distribution ($\beta$ = $100$ and $\alpha$ = $5$).
This low evolutionary rate values allowed to reduce the number of homoplasic character changes and thus reinforce the phylogenetic information in the matrices (see supplementary materials @@@).
We resimulated every invariant characters to obtain a matrix with no invariant characters.
To ensure the that our simulation where reflecting the same parameters as real data, we only selected matrices with Consistency Indices superior to $0.26$ \citep{OReilly20160081}.
